### 2016-04-22 thesis/methods/methods.tex
started writing up a summary in prep to committee meeting; some work done on the thesis

\chapter{Methods}
\label{ch:methods}

@@

The clinical data for all cancer types (33 types in total) were downloaded from TCGA database and were checked for the height and weight data for each sample.
Any cancer type with no weight and/or height data of the samples were excluded from the project, as no BMI information can be obtained without these data.
This gave a total of eight cancer types (**insert all the names of cancer types here) to be used for further analyses.

@@

The raw microarray data for all 103 samples in the study were normalised using Robust Multi Array (RMA) method from the \textit{affy} package in R.

@@

The process above was repeated on the same data, with same group (obese and non-obese) after controlling for all other clinical variables that were not related to the sample BMI (age, sex, race, tumour grade, lymph node (LN) status, progesterone receptor (PR) status, and estrogen receptor (ER) status).
The top 799 differentially expressed gene probes that had p-value \textless{} 0.01 between the two groups were identified.

>>>>

\chapter{Methods (draft)}
\label{ch:methods}

@@

The clinical data for all cancer types (33 types in total) were downloaded from TCGA database and were checked for the height and weight data for each sample.
Any cancer type with no weight and/or height data of the samples were excluded from the project, as no BMI information can be obtained without these data.
This gave a total of eight cancer types (bladder urothelial carcinoma (BLCA), cervical squamous cell carcinoma and endocervical adenocarcinoma (CESC), colon adenocarcinoma (COAD), kidney renal clear cell carcinoma (KIRP), liver hepatocellular carcinoma (LIHC), rectum adenocarcinoma (READ), skin cutaneous melanoma (SKCM), and uterine corpus endometrial carcinoma (UCEC)) to be used for further analyses.

@@

The raw microarray data for all 103 samples in the study were normalised using Robust Multi Array (RMA) method from the \textit{affy} package in R.
The data was then standardised so that each of the genes had a mean of 0 and a standard deviation of 1.
(mention scaling anything over 3 were made to be 3 for heatmap scaling)

@@

The process above was repeated on the same data, with the same group (obese and non-obese) after controlling for all other clinical variables that were not related to the sample BMI (age, sex, race, tumour grade, lymph node (LN) status, progesterone receptor (PR) status, and estrogen receptor (ER) status).
The top 799 differentially expressed gene probes that had p-value \textless{} 0.01 between the two groups were identified.

### 2016-04-22 thesis/results/results.tex
started writing up a summary in prep to committee meeting; some work done on the thesis

\chapter{Results from \citet{Creighton2012} metagene}

\section{SVD}

>>>>

\chapter{Results from \citet{Creighton2012} metagene (draft)}

\section{Validation of previously identified obesity-associated genetic signatures}

(draft)\\
To validate the ability for the obesity-associated biomarkers to categorise the obese samples from non-obese samples, singular value decomposition with the previously identified 799 gene probes was used on the raw data.
The metagene produced from this was used to check whether the obesity-associated biomarkers were able to identify the difference in obesity groups within the samples.
(insert first figure - gene expression sorted by metagene)
The resulting heatmap shown in figure~(fig:crobsheat) shows how the overall gene expression of each sample is represented well by the metagene created from the 799 gene probes identified by \citet{Creighton2012}.

To assess whether the metagene was actually correlating with the sample BMI values and statuses, a scatter plot and a box plot were plotted against the metagene, respectively.
These plots proved that the obesity-associated signatures identified by \citet{Creighton2012} were able to classify the samples based on their BMI status (specifically the obese samples from the non-obese samples), confirming the results fromthe study.

\section{Reproducing the obesity-associated genetic signatures}

(draft - are we able to find the same/similar genes as creighton, using the same data?)\\
To see whether we were able to re-identify the same, or similar, gene probes as \citet{Creighton2012}, differential gene expression analyses were carried out between the obese and non-obese samples, with different statistical conditions.

\section{Application of the obesity-associated genetic signatures to other cancer types}

(draft - found nothing)

\section{\citet{Fuentes-Mattei2014} gene signatures on \citet{Creighton2012} data and vice versa}

(draft)

\section{\citet{Fuentes-Mattei2014} gene signatures on TCGA data and vice versa}

(draft)
